Discussion

### 2023-06-29 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
reshaped a sentence

The present Registered Report was designed to assess whether our new Cognitive and Affective Discounting (CAD) paradigm is suitable for determining individual subjective values of the ER strategies distraction, distancing, and suppression.
We adapted Westbrook et al.'s[-@Westbrook2013] Cognitive Effort Discounting paradigm in a way that allows SVs to be determined for tasks without objective difficulty order. 
The new paradigm was tested on an *n*-back task[@ZernaScheffel2022] and a classic ER paradigm.
The latter was the goal of the present study and completed by $N=`r sum(data_survey[,"followup_ered_complete"] == 2)-1`$ participants. 
As expected, the use of ER strategies was associated with reduced subjective and physiological arousal.
This finding is in line with previous meta-analytic findings indicating the effectiveness of ER strategies, both on subjective as well as physiological levels[@Webb2012;@Zaehringer2020].
Furthermore, we found higher levels of subjective cognitive effort for all ER strategies compared to active viewing. 
This allows us to replicate previous findings from our research group and show that strategy use is associated with cognitive effort[@Scheffel2021].
Both measures also showed high variability between individuals.
Taken together, this means that the ER strategies had the intended effect on the participants: Individuals were able to effectively reduce subjective and physiological responding at the expense of cognitive effort.
It was nevertheless surprising that the strategy suppression showed on average and descriptively the lowest *corrugator* activity, the lowest effort ratings and the highest utility ratings. 
In the case of the EMG measurement, this could be due to the fact that the result of the implementation of the instructions ("Maintain a neutral facial expression") is measured directly. 
The direct instruction also reduces the complexity of the generation process, which is why the required effort is the lowest.
By comparison, distancing increases the complexity, because it requires an impersonal reappraisal of the stimulus.
Ultimately, the immediacy and simplicity are then expressed in terms of greater subjective utility of the strategy. 
In addition, one receives relatively direct feedback from one's own facial muscle activity as to how well the strategy suppression has been implemented.
In the case of the strategies distraction and distancing, a more detailed evaluation of internal states must take place in order to assess their utility, which again requires more effort.
Since the manipulation checks were successful, the subjective and physiological measures were likely to be meaningful in influencing the individual SVs.

@@

In order to gain a more comprehensive picture of ER, dynamic or cyclic processes have to be considered.
The extended process model of emotion regulation[@Gross2015] postulates three sequential stages, namely identification, selection, and implementation, to achieve a given goal in a situation.
If the regulatory goal is not achieved, the ER strategy can be maintained, switched or stopped[@Gross2015].
Importantly, the information about the success of implementing an ER strategy influences the choice of ER strategies in future situations, because the regulation context is changed through contextual feedback [@Gross2015;@AldaoChristensen2015;@Murphy2018;@Sheppes2020].
This means that studies on ER Choice should consider not only situational factors, but also contextual factors[@Murphy2018].
For example, in a classic ER choice paradigm[@Sheppes2011], Murphy and Young[-@Murphy2018] showed that strategy choice was significantly influenced by strategy choice and negative affect in the previous trial.
This provides empirical evidence that experience gained during use of ER strategies influences future choice of ER strategies.
Our newly developed CAD paradigm also makes an important contribution here.
The information and experiences that participants gain while using the strategies in the experimental task might be implicitly incorporated into the subsequent calculation of SVs.
That is, the participants first apply all the strategies and then make the monetary decisions while expecting that they should repeat the strategies again.
This raises the question of how stable these individual SVs are.

@@

Knowing whether SVs of ER strategies show a trait character would allow to further evaluate the relevance of the calculated SVs.
However, whether the calculated values represent a stable value within the individual cannot be concluded from the present study alone.
To establish the *trait* nature of a measure, one could for instance resort to latent state trait modeling[@Steyer2015], as recently employed by our group in a related context[@Strobel2020].
The individual SVs calculated in our CAD paradigm were assessed in the laboratory in a single situation. 
By definition, this represents a state.
As noted above, personal regulatory goals, situational factors, and contextual demands influence the choice for or against ER strategies[@Aldao2015;@Bonanno2013@Sheppes2011;@Scheffel2021;@Haines2016].
We believe that these goals, factors, and demands also influence individual SVs of ER strategies.
Our data presented in this study support this idea.
However, this also implies that SVs should differ according to situational factors (e.g. stimulus intensity).
The ER goals that individuals pursue in a given situation must also be taken into account.
In our laboratory setting, participants mainly pursue prohedonic goals, but certainly not social goals[@Tamir2016].
Wilms and colleagues[-@Wilms2020] pointed out that ER goals, as well as situational factors, should be treated as states, because both vary greatly from event to event and situation to situation.
In a different situation, for example outside the laboratory, where an individual is primarily pursuing a social goal, a different strategy might appear more helpful and thus have a higher SV.
It should also be noted that the calculation of individual SVs in our CAD paradigm always refers to the alternative strategies that were available to the individuals (see also [Limitations](#Limitations)).
Therefore, SVs may vary when different reference strategies are used.
It is conceivable that SVs are likely to be highly correlated in situations with similar demands and goals. 
They would thus reflect habits or habitual use of ER strategies, which has already been attempted to capture by means of questionnaires[@GrossJohn2003]. 
Of course, it is also possible that such habits influence the internal formation of these subjective values.
However, our data are not suitable for answering this question.
In the future, SVs should therefore be collected in several similar situations. 
Subsequently, the association of the values with each other could be assessed, as well as correlations with relevant external criteria, such as well-being[@GrossJohn2003].

@@

In order to cope with changing emotional demands, individuals may flexibly select and apply ER strategies from their repertoire[@Bonanno2013;@Aldao2015].
The strategy that is most suitable for coping with contextual demands and achieving regulatory goals is selected[@Aldao2015;@Tamir2016].
The combination of influencing factors should be reflected in subjective values that are formed for all alternatives and serve as a basis for decision-making.
To date, such subjective values have not been established for ER strategies.
Our proposed CAD paradigm contributes to research on ER Choice and ER Flexibility by allowing quantification of these values. 
This further enables to investigate in more detail the factors influencing the internal generation of these subjective values of ER strategies.
It appears that the subjective value attributed to a strategy is primarily determined by perceived usefulness and effort.
Finally, further research is needed to investigate the factors that influence subjective values and whether these values represent habitual use of ER strategies by individuals.

>>>>

The present Registered Report was designed to assess whether our new Cognitive and Affective Discounting (CAD) paradigm is suitable for determining individual subjective values of the ER strategies distraction, distancing, and suppression.
We adapted Westbrook et al.'s[-@Westbrook2013] Cognitive Effort Discounting paradigm in a way that allows SVs to be determined for tasks without objective difficulty order. 
The new paradigm was tested on an *n*-back task[@ZernaScheffel2022] and a classic ER paradigm.
The latter was the goal of the present study and completed by $N=`r sum(data_survey[,"followup_ered_complete"] == 2)-1`$ participants. 
As expected, the use of ER strategies was associated with reduced subjective and physiological arousal.
This finding is in line with previous meta-analytic findings indicating the effectiveness of ER strategies, both on subjective as well as physiological levels[@Webb2012;@Zaehringer2020].
Furthermore, we found higher levels of subjective cognitive effort for all ER strategies compared to active viewing. 
This allows us to replicate previous findings from our research group and show that strategy use is associated with cognitive effort[@Scheffel2021].
The measures of arousal and effort also showed high variability between individuals.
Taken together, this means that the ER strategies had the intended effect on the participants: Individuals were able to effectively reduce subjective and physiological responding at the expense of cognitive effort.
It was nevertheless surprising that the strategy suppression showed on average and descriptively the lowest *corrugator* activity, the lowest effort ratings and the highest utility ratings. 
In the case of the EMG measurement, this could be due to the fact that the result of the implementation of the instruction ("Maintain a neutral facial expression") is measured directly. 
The direct instruction also reduces the complexity of the generation process.
This could be why the required subjective effort is the lowest.
Finally, immediacy and simplicity are expressed as greater subjective utility of the strategy suppression.
In addition, one receives relatively direct feedback from one's own facial muscle activity as to how well suppression has been implemented.
In contrast, the strategies distraction and distancing require a more detailed evaluation of internal states in order to assess their utility, which in turn requires more effort.

@@

In order to gain a more comprehensive picture of ER, dynamic or cyclic processes have to be considered.
The extended process model of emotion regulation[@Gross2015] postulates three sequential stages, namely identification, selection, and implementation, to achieve a given goal in a situation.
If the regulatory goal is not achieved, the ER strategy can be maintained, switched or stopped[@Gross2015].
Importantly, the information about the success of implementing an ER strategy influences the choice of ER strategies in future situations, because the regulation context is changed through contextual feedback [@Gross2015;@AldaoChristensen2015;@Murphy2018;@Sheppes2020].
This means that studies on ER Choice should consider not only situational factors (i.e., perceived control, emotional intensity[@Wilms2020]), but also contextual factors (i.e., state-dependent psychological processes of the participant and task characteristics; for a review, see Aldao, 2013[@Aldao2013])[@Murphy2018].
For example, in a classic ER choice paradigm[@Sheppes2011], Murphy and Young[-@Murphy2018] showed that strategy choice was significantly influenced by strategy choice and negative affect in the previous trial.
This provides empirical evidence that experience gained during use of ER strategies influences future choice of ER strategies.
Our newly developed CAD paradigm also makes an important contribution here.
The information and experiences that participants gain while using the strategies in the experimental task might be implicitly incorporated into the subsequent calculation of SVs.
That is, the participants first apply all the strategies and then make the monetary decisions while expecting that they should repeat the strategies again.
This raises the question of how stable these individual SVs are.

@@

Knowing whether SVs of ER strategies show a trait character would allow to further evaluate the relevance of the calculated SVs.
However, whether the calculated values represent a stable value within the individual cannot be concluded from the present study alone.
To establish the *trait* nature of a measure, one could for instance resort to latent state trait modeling[@Steyer2015], as recently employed by our group in a related context[@Strobel2020].
However, this would require at least two measurements of SVs.
The individual SVs calculated in our CAD paradigm were assessed in the laboratory in a single situation. 
By definition, this represents a state.
As noted above, personal regulatory goals, situational factors, and contextual demands influence the choice for or against ER strategies[@Aldao2015;@Bonanno2013@Sheppes2011;@Scheffel2021;@Haines2016].
We believe that these goals, factors, and demands also influence individual SVs of ER strategies.
Our data presented in this study support this idea.
However, this also implies that SVs should differ according to situational factors (e.g. stimulus intensity).
The ER goals that individuals pursue in a given situation must also be taken into account.
In our laboratory setting, participants mainly pursue prohedonic goals, but certainly not social goals[@Tamir2016].
Wilms and colleagues[-@Wilms2020] pointed out that ER goals, as well as situational factors, should be treated as states, because both vary greatly from event to event and situation to situation.
In a different situation, for example outside the laboratory, where an individual is primarily pursuing a social goal, a different strategy might appear more helpful and thus have a higher SV.
It should also be noted that the calculation of individual SVs in our CAD paradigm always refers to the alternative strategies that were available to the individuals (see also [Limitations](#Limitations)).
Therefore, SVs may vary when different reference strategies are used.
It is conceivable that SVs are likely to be highly correlated in situations with similar demands and goals. 
They would thus reflect habits or habitual use of ER strategies, which has already been attempted to capture by means of questionnaires[@GrossJohn2003]. 
Of course, it is also possible that such habits influence the internal formation of these subjective values.
However, our data are not suitable for answering this question.
In the future, SVs should therefore be collected in several similar situations. 
Subsequently, the association of the values with each other could be assessed, as well as correlations with relevant external criteria, such as well-being[@GrossJohn2003].

@@

In order to cope with changing emotional demands, individuals may flexibly select and apply ER strategies from their repertoire[@Bonanno2013;@Aldao2015].
The strategy that is most suitable for coping with contextual demands and achieving regulatory goals is selected[@Aldao2015;@Tamir2016].
The combination of influencing factors should be reflected in subjective values that are formed for all alternatives and serve as a basis for decision-making.
To date, such subjective values have not been established for ER strategies.
Our proposed CAD paradigm contributes to research on ER Choice and ER Flexibility by allowing quantification of these values. 
This further enables to investigate the factors influencing the internal generation of these subjective values of ER strategies in more detail.
It appears that the subjective value attributed to a strategy is primarily determined by perceived usefulness and effort.
Finally, further research is needed to investigate the factors that influence subjective values and whether these values represent habitual use of ER strategies by individuals.

### 2023-06-29 06_Paper/ER-ED/ERED_Stage2/method.Rmd

*Subjective values of emotion regulation strategies.* <br> For each ER strategy, SVs were calculated as follows: first, the value 0.02€ was added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
Second, to obtain the SV of the fixed strategy (the minimum relative reward required for participants to choose the flexible over the fixed strategy), the last value of the flexible strategy was divided by 2€.
Therefore, the SVs of the flexible strategies were 1, because they were chosen in the initial comparison of each pairing in which the same value was offered for both strategies, so they were the preferred strategy of each pairing.
The SVs of the fixed strategies lay between 0 and 1, with lower values indicating that the participant would need a much higher monetary incentive to choose this strategy over the other one in the pairing. 
The final SV per strategy for each participant was computed by averaging the SVs of each strategy across pairings.

>>>>

*Subjective values of emotion regulation strategies.* <br> For each ER strategy, SVs were calculated as follows: first, the SV of the flexible strategy was set to 1, because in the first comparison of each pairing where the same value was offered for both strategies, so the flexible strategy was the preferred strategy in each pairing.
Second, to obtain the SV of the fixed strategy (the minimum relative reward required for participants to choose the flexible strategy over the fixed strategy), the value 0.02€ was added to or subtracted from the last monetary value of the flexible strategy, depending on the participant's last choice.
The resulting value of the flexible strategy was divided by 2€.
This yielded an SV of the fixed strategy between 0 and 1, with values closer to 0 indicating a stronger aversion to the fixed strategy compared to the flexible strategy.
The final SV per strategy for each participant was computed by averaging the SVs of each strategy across pairings.
